Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-30 kappa.tex
Improve paleo-glaciation plot.

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of the last glacial maximum northern hemisphere ice
           sheets, after \citep{Ehlers.Gibbard.2007}.
           \todo{Rotate by 90\degree, re-centre, and compare with present-day
           ice cover. Maybe label the major ice sheets: CIS, LIS, GIS, FIS...}}
  \label{fig:palaeo-glaciation}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present, and \textbf{(b)} during the last
           glacial maximum \citep{Ehlers.Gibbard.2007}. Coastlines and present
           glaciers are made with Natural Earth \citep{Patterson.Kelso.2014}.}
  \label{fig:palaeo-glaciation}
\end{figure}
